Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-04-28 paper.tex
Minor typo fixes

The kernel latency of m-mapping a memory region is lowest when the new memory is allocated
next to an already allocated region. This latency is the worst in the frag microbenchmark i.e., when an already mapped region
is to be expanded. We suspect a lot of real world applications to show the fragmented 
behavior since it is common for applications to exapnd their existing data structures. 
This finding highlights
the imporance of optimistically leaving empty spaces around the allocated regions to 
speed up memory expension. This practice would particularly be useful for performance crucial applications
running atop compute infrastructures where memory is not a scarce resource, but kernel is.

>>>>

The kernel latency of creating a memory region is lowest when the new memory is
allocated next to an already allocated region. This latency is the worst in the
\texttt{frag} microbenchmark i.e., when an already mapped region is to be expanded. We
suspect a lot of real world applications to show the fragmented behavior since
it is common for applications to exapnd their existing data structures.  This
finding highlights the imporance of optimistically leaving empty spaces around
the allocated regions to speed up memory expension. This practice would
particularly be useful for performance crucial applications running atop compute
infrastructures where memory is not a scarce resource, but kernel is.

(TODO: (markm) I am hesitant about these conclusions...)
